# pre-class


Make sure you commit this often with meaningful messages. 



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


1. Read the source code for each of the following three functions, puzzle out what they do, and then brainstorm better names.

```
f1 <- function(string, prefix) {
  substr(string, 1, nchar(prefix)) == prefix
}
#Better name for f1 is prefix_pull

f2 <- function(x) {
  if (length(x) <= 1) return(NULL)
  x[-length(x)]
}
#Better name for f2 is trim_last

f3 <- function(x, y) {
  rep(y, length.out = length(x))
}
#Better name for f3 is repeat_x_len_y
```

2. Compare and contrast rnorm() and MASS::mvrnorm(). How could you make them more consistent?
#mvrnorm is the multivariate version of rnorm and uses the variance-covariance matrix in place of rnorm's sd. 


3. Use `lapply()` and an anonymous function to find the coefficient of variation (the standard deviation divided by the mean) for all columns in the mtcars dataset. 

```{r}
mtcars <- mtcars
coeff_variation <-lapply(mtcars, function(x) sd(x)/mean(x))
coeff_variation
```

4. Use vapply() to:
    a. Compute the standard deviation of every column in a numeric data frame.
```{r}
df <- data.frame(replicate(10,sample(0:1,1000,rep=TRUE)))
col_sd <- vapply(df, sd, numeric(1))
col_sd
```

    b. Compute the standard deviation of every numeric column in a mixed data frame. (Hint: you'll need to use vapply() twice.)
```{r}
vapply(iris[vapply(iris, is.numeric, logical(1))],
       sd,
       numeric(1))
```